% \vspace{-0.8em}
\section{Introduction}
% \vspace{-0.8em}
Stochastic timed systems are systems that exhibit both timed and stochastic behaviours.
Such systems play a dominant role in many real-world applications (cf.~\cite{DBLP:books/daglib/0020348}), hence
addressing fundamental issues such as safety and performance over these systems are important.
\emph{Probabilistic timed automata} (PTAs)~\cite{DBLP:journals/fmsd/NormanPS13,DBLP:journals/tcs/Beauquier03,DBLP:journals/tcs/KwiatkowskaNSS02} serve as a good mathematical model for these systems.
They extend the well-known model of timed automata~\cite{DBLP:journals/tcs/AlurD94} (for nonprobabilistic timed systems) with discrete probability distributions, and Markov Decision Processes (MDPs)~\cite{PutermanMDP} (for untimed probabilistic systems) with timing constraints.

Formal verification of PTAs has received much attention in recent years~\cite{DBLP:journals/fmsd/NormanPS13}.
For branching-time model checking of PTAs, the problem is reduced to computation of reachability probabilities over MDPs through well-known finite abstraction for timed automata (namely \emph{regions} and \emph{zones})~\cite{JensenPTA,DBLP:journals/tcs/Beauquier03,DBLP:journals/tcs/KwiatkowskaNSS02}.
Advanced techniques for branching-time model checking of PTAs such as inverse method and symbolic method have been explored in  ~\cite{DBLP:journals/fmsd/AndreFS13,DBLP:journals/iandc/KwiatkowskaNSW07,DBLP:conf/formats/KwiatkowskaNP09,DBLP:conf/formats/JovanovicKN15}.
Extension with \emph{cost} or \emph{reward}, resulting in \emph{priced} PTAs, has also been investigated.
On one hand, Berendsen \emph{et al.}~\cite{DBLP:conf/tamc/BerendsenCJ09} proved that cost-bounded reachability probability is undecidable over priced PTAs.
On the other hand, Jurdzinski~\emph{et al.}~\cite{DBLP:conf/concur/JurdzinskiKNT09} and Kwiatkowska~\emph{et al.}~\cite{DBLP:journals/fmsd/KwiatkowskaNPS06} proved that several notions of accumulated (discounted) cost are computable over priced PTAs.
Most verification algorithms for PTAs have been implemented in the model checker PRISM~\cite{DBLP:conf/cav/KwiatkowskaNP11}. Computational complexity of several verification problems for PTAs is studied in~\cite{DBLP:journals/ipl/LaroussinieS07,DBLP:journals/lmcs/JurdzinskiSL08,DBLP:conf/concur/JurdzinskiKNT09}.

A shortcoming of existing verification approaches for PTAs is that they all considered branching-time properties.
As far as we know, no results have ever considered linear-time model checking for PTAs.
Linear-time temporal properties are however important as they can specify complex timed behaviours induced by e.g. finite sequences of timed events.
In particular, we focus on linear-time temporal properties that can be encoded by deterministic timed automata (DTAs).
DTA is the deterministic version of timed automata.
Although DTA is weaker than general timed automata, it can recognize a wide class of formal timed languages, and express interesting properties which cannot be expressed in branching-time logics~\cite{DBLP:journals/tse/DonatelliHS09}.
The problem to verify DTA-specifications over stochastic timed models has only been investigated for continuous-time Markov processes (cf.~\cite{DBLP:journals/tse/DonatelliHS09,DBLP:journals/corr/abs-1101-3694,DBLP:conf/hybrid/Fu13,DBLP:conf/hybrid/BrazdilKKKR11,DBLP:conf/tacas/BarbotCHKM11,DBLP:conf/formats/BortolussiL15}), a completely different formalism for stochastic timed systems which assigns probability distributions to time elapses.
In this paper, we study verification of DTA-specifications over PTAs.
As far as we know, we are the first to conduct this line of research.

\textbf{Our Contributions.} We show that through a product construction, the optimal probability of PTA-paths accepted by a DTA w.r.t the finite acceptance criterion can be computed exactly by known algorithms for reachability probabilities over PTAs.
The novelty of our product construction is that to enable the DTA to keep track of the next location after a probabilistic jump in the PTA, one needs to integrate either the set of regions of the DTA or a local conjunction over the rules of the DTA.
%Then we show that migrating from finite acceptance criteria to Rabin criteria can be handled by maximal end components. Finally, we show that under almost-sure acceptance w.r.t finite acceptance condition, the expected accumulated cost/reward until acceptance can be computed through known algorithms for priced PTAs.
We demonstrate experimental results on several case studies and show that our approach is effective to analyse linear-time properties over PTAs.
%\textbf{Organization of the Paper.} Section~\ref{?} introduces some preliminaries. Section~\ref{?} describes the problem studied in this paper. Section~\ref{} is the core part of this paper which demonstrates the product construction.
%Section~\ref{?} illustrates several case studies.
%Finally, Section~\ref{?} show our experimental results and Section~\ref{?} concludes the paper.